\section{Classes}

A class is a static 
%off-line \todo{es realmente off-line?}
template from which objects are 
created. Classes are used 
to classify objects  
that define 
common operations 
and a data structure, 
and the data types
that the object can 
store.\\

To give a concrete example, this section 
focuses on data acquisition model of 
the current transformer and their 
(conveniently abbreviated TCTR 
for this chapter). 
The datas of switchyard functionalities, 
such as {TCTR}, depends of 
each specific situation. Then, 
the {TCTR} should be modelled as 
a class, i.e., a static template  
which diferents current transformer objects 
are created. The same reasoning might be 
applied to the Disconnecting Switches 
(by convention, here called {XSWI})
and circuit breakers ({XCBR}).

\todo[inline]{aqui ira el  codigo de estos nodos logicos, escrito en java}

%Codigo fuente
%C:\Documents and Settings\DELL\Mis
%documentos\tesismayo\tesismayo\thesis\chapters\ch-oop\source\java\src\HelloWorld.java
%\lstinputlisting[label=samplecode,caption=A sample]{sourceCode/HelloWorld.java}
%chapters\ch-oop\source\java\src\HelloWorld.java

\lstinputlisting[label=code:TCTR_v1java,
caption=TCTR class in Java]{chapters/ch-oop/source/java/src/TCTR_v1.java}

\\

\lstinputlisting[label=code:XSWI_v1java,
caption=XSWI class in Java]{chapters/ch-oop/source/java/src/XSWI_v1.java}

\\ 

\lstinputlisting[label=code:XCBR_v1java,
caption=XCBR class in Java]{chapters/ch-oop/source/java/src/XCBR_v1.java}

\lstinputlisting[label=code:TVoltageLevel_v1java,
caption=Voltage Level class 
in Java]{chapters/ch-oop/source/java/src/TVoltageLevel_v1.java}



%\lstinputlisting[label=codeClass,
%caption=Class in Java]{chapters/ch-oop/source/java/src/SERVER_v1.java}

%%TODO: cite adobe book

\subsection{Attributes}
\todo[inline]{completar esta parte}
%	\lstinputlisting[label=codeAttributes,
%	caption=Class with attributes in Java]
%	{chapters/ch-oop/source/java/src/SERVER_v2.java}
	\lstinputlisting[label=codeMethodr,
	caption=Class with attributes and methods in Java]
	{chapters/ch-oop/source/java/src/TSubstation_v2.java}



\subsection{Methods}
Methods are functions that are part of a class 
definition. Once an instance of the class is created, 
a method is bound to that instance.\\
	\lstinputlisting[label=codeMethodr,
	caption=Class with attributes and methods in Java]
	{chapters/ch-oop/source/java/src/SERVER_v2.java}



	\subsubsection{Get and set accessor methods}
	Get and set accessor functions, also called getters 
	and setters, allow you to adhere to the programming principles of 
	information hiding and encapsulation while providing an 
	easy-to-use programming interface for the classes that you 
	create. Get and set functions allow you to keep your class 
	properties private to the class, but allow users of your class 
	to access those properties as if they were accessing a 
	class variable instead of calling a class method. 
	The advantage of this approach is that you can avoid 
	having two public-facing functions for each property 
	that allows both read and write access. \\

		\lstinputlisting[label=codeMethods,
		caption=Class with attributes, methods, getters and setters in Java]
		{chapters/ch-oop/source/java/src/SERVER_v4.java}
	
	
	\subsubsection{Constructor methods}
	Constructor methods, sometimes simply called constructors, 
	are functions that share the same name as the class in 
	which they are defined. Any code that you include in 
	a constructor method is executed whenever an instance of the 
	class is created with the  new  keyword. \\

		\lstinputlisting[label=codeMethodt,
		caption=Class with attributes, methods, 
		getters, setters and constructors in
		Java] {chapters/ch-oop/source/java/src/SERVER_v5.java}

	
